%------------------------
% Latex CV Template - Ignacio Romero Aravena (English Version)
%------------------------

\documentclass[letterpaper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{changepage}

% Formatting
\setlist{noitemsep}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}
\newenvironment{subs}
{\adjustwidth{2em}{0pt}}
{\endadjustwidth}

%-------------------------------------------------------------------------------
\begin{document}
	
	\pagestyle{empty}
	
	% Header
	\begin{center}
		\textbf{\Large IGNACIO ROMERO ARAVENA}\\[3pt]
		\textbf{Santiago, Chile}\\[1pt]
		\href{mailto:ignacio.romero.a@ug.uchile.cl}{ignacio.romero.a@ug.uchile.cl} | \href{https://tnacho-23.github.io}{tnacho-23.github.io} | +56 9 7131 1032
	\end{center}
	
	%------------------------
	\section*{ABOUT ME}
	Electrical Engineering student at the University of Chile with a strong interest in robotics, computational intelligence, and project management. Experienced student leader, university teaching assistant, and active member of research and robotics teams. I complement my academic background with competitive sports and community service. Characterized by commitment, proactivity, and teamwork across all collaborative projects.
	
	%------------------------
	\section*{EDUCATION}
	
	\noindent
	\textbf{B.S. \& M.S. in Electrical Engineering} \\
	2020 - Present \\ 
	University of Chile \\ 
	Faculty of Physical and Mathematical Sciences \\
	\\
	
	\noindent
	\textbf{High School Diploma} \\
	Graduated 2019 \\ 
	Colegio San Marcos de Arica \\ 
	Arica, Chile.
	
	%------------------------
	\section*{EXPERIENCE}
	
	\noindent
	\textbf{Teaching Assistant} \\
	2022 - Present \\
	Santiago, Chile \\ 
	Assistant for courses in Project Management and Teamwork, Computational Intelligence, Image Processing, and Robotics \& Automation. I facilitate learning in specialized laboratories and core courses, introducing research methodologies, fostering collaboration in innovation projects, and guiding technical development in autonomous vehicles, AI, and advanced programming for undergraduate and graduate students.
	
	\noindent
	\textbf{Internship - Advanced Mining Technology Center (AMTC)} \\
	December 2024 - February 2025 \\
	Santiago, Chile \\ 
	Designed an object classification system using Continual Learning within an R\&D center focused on mining technology. \\
	
	\noindent
	\textbf{Team Leader - ElectroTutores} \\
	2024 - Present \\
	University of Chile \\ 
	Responsible for the academic organization of the Department of Electrical Engineering and student outreach/engagement. \\
	
	\noindent
	\textbf{Internship - Sistemo} \\
	January 2023 - February 2023 \\
	Santiago, Chile \\ 
	Performed preventive and corrective maintenance (software and hardware) on robotic logistics and distribution systems. \\
	
	%------------------------
	\section*{PROJECTS AND VOLUNTEERING}
	\begin{itemize}
		\item \textbf{Uchile Robotics Team:} Active member of "Uchile Homebreakers" and assistant at the robotics laboratory.
		\item \textbf{Santiago 2023 Volunteer:} English/Spanish interpreter and management staff at the Pan American Village.
		\item \textbf{FCFM University Induction:} Mentor and group leader for incoming freshmen (2022-2023).
		\item \textbf{Arica Youth Ministry:} Coordinator of voluntary activities for children and youth (2015-2020).
	\end{itemize}
	
	%------------------------
	\section*{SKILLS AND CERTIFICATIONS}
	\begin{subs}
		\textbf{Languages:} English (Intermediate-Advanced; TOEFL ITP: 623 pts; Cambridge FCE B2). \\
		\textbf{Technical Skills:} ROS (Robot Operating System), Software Programming, Machine Learning, 3D Modeling \& Printing, Circuit Design, Advanced Image Processing. \\
		\textbf{Software:} Microsoft Office, Google Workspace, Microcontroller Programming.
	\end{subs}
	
	%------------------------
	\section*{PUBLICATIONS}
	\begin{subs}
		\textbf{Continual Object Learning Using Gaussian Modeling.} \\
		Romero, I., Loncomilla, P., \& Ruiz-del-Solar, J. \\
		En: \textit{Image Analysis and Processing – ICIAP 2025 Workshops}. Lecture Notes in Computer Science (LNCS). Springer, Cham (2026). \\
		DOI: \href{https://doi.org/10.1007/978-3-032-11381-8_16}{10.1007/978-3-032-11381-8\_16}
	\end{subs}
	
	
	%------------------------
	%\section*{REFERENCES}
	%\noindent
	%\textbf{Dr. Javier Ruiz del Solar} \\
	%Internship Supervisor and Thesis Advisor, AMTC. \\
	%\href{mailto:jruizd@ing.uchile.cl}{jruizd@ing.uchile.cl} \\
	
	%\noindent
	%\textbf{Prof. Andrés Caba Rutte} \\
	%Head of Studies, Department of Electrical Engineering, University of Chile. \\
	%\href{mailto:acaba@ing.uchile.cl}{acaba@ing.uchile.cl}
	
\end{document}